---
title: "Text Minning in R"
author: "Upal Chowdhury"
date: "September 22, 2016"
output: html_document
---
#Getting Unstructured Data and loading necessary library
```{r v}
library(readr)
library(stringr)
library(knitr)
library(RCurl)
data <- data.frame(read_csv("C:/Users/upalchow/Desktop/cuny_sps_fall2016/Data-607/MSDA-607/tournamentinfo.txt", skip = 3))
head(data)
```
##Extracting player name
```{r eval = T}
name <- unlist(str_extract_all(data,"\\| [[:upper:]- ]{4,} \\|"))
name <- str_replace_all(name,"(\\| )|([[:space:]]{1,}\\|)","")
head(name)
```
##Reading data again with different reader for extracting state using regular expression
```{r eval = T}
data <- read.table("C:/Users/upalchow/Desktop/cuny_sps_fall2016/Data-607/MSDA-607/tournamentinfo.txt",header = FALSE,sep = ",",skip = 4,stringsAsFactors = F)
#extracting
state <- unlist(str_extract_all(data, "[[:upper:]]{2}[[:space:]]\\|"))
#replacing symbols, spaces with empty string
state <- str_replace_all(state,"[[:space:]]{1,}\\|", "")
head(state)
tail(state)
```


#Checking if same length was extracted for this two variable by creating a df
```{r eval = T}
name_and_state <- data.frame(cbind(name,state))
head(name_and_state)
```

#Extracting  players point
```{r eval = T}
point <- unlist(str_extract_all(data,"\\|[[:digit:].[:digit:]]{3}[[:space:]]{1,}\\|"))
point <- str_replace_all(point,"(\\|)|([[:space:]]{1,}\\|)","")
name_and_state_points <- data.frame(cbind(name,state,point))
head(name_and_state_points)
```

# Extracting Player's Pre-Rating
```{r eval = T}
pre_rating <- unlist(str_extract_all(data, "[:] [[:alnum:] ]{2,9}\\-\\>"))
pre_rating <- str_replace_all(pre_rating,"(\\: )|([[:space:]]{1,}\\-\\>)","")
#since some of the extracted rating has alpha attached , need to be removed and converting to numeric
pre_rating <- as.numeric(str_replace_all(pre_rating,"([A-Z][[:digit:]]{1,2})|(\\-\\>)",""))
tail(pre_rating,7)
```

#  Average Pre Chess Rating of Opponents

## *For this last column it was found convenient to use read.table reader with additional parametere*
```{r eval = T}
newdata <-
  read.table(
  "C:/Users/upalchow/Desktop/cuny_sps_fall2016/Data-607/MSDA-607/tournamentinfo.txt",
  header = FALSE,
  sep = "|",
  skip = 4,
  stringsAsFactors = FALSE,
  fill = TRUE
  )
str(newdata)
tail(newdata,3)
```

#Creating round 1 to round 7 vector of opponents in order use them in calculating Average Pre Chess Rating of Opponents
```{r eval = T}
R1 <- (str_extract(newdata$V4[c(TRUE, FALSE, FALSE)], "\\d+"))
R2 <- (str_extract(newdata$V5[c(TRUE, FALSE, FALSE)], "\\d+"))
R3 <- (str_extract(newdata$V6[c(TRUE, FALSE, FALSE)], "\\d+"))
R4 <- (str_extract(newdata$V7[c(TRUE, FALSE, FALSE)], "\\d+"))
R5 <-  (str_extract(newdata$V8[c(TRUE, FALSE, FALSE)], "\\d+")) 
R6 <-  (str_extract(newdata$V9[c(TRUE, FALSE, FALSE)], "\\d+"))
R7 <-  (str_extract(newdata$V10[c(TRUE, FALSE, FALSE)], "\\d+"))
```

# Creating data frame with new variables
```{r eval = T}
df <- data.frame(cbind(name,state,point,pre_rating,R1,R2,R3,R4,R5,R6,R7))
head(df)
str(df)
```

#adding player number to indexing the pre_rating of opponents
```{r eval = T}
player_num <- unlist(str_extract_all(data, "\\d{1,2}\\s\\|"))
player_num <- str_replace_all(player_num,"(\\s\\|)","")
player_num <- as.numeric(player_num)
head(player_num)
```


```{r eval = T}
df <- data.frame(cbind(player_num,name,state,point,pre_rating,R1,R2,R3,R4,R5,R6,R7),stringsAsFactors = FALSE)
attach(df)
```

#looping through each row of the data frame in order to replace the opponent id with their respective pre_rating score
```{r eval = T}
for (i in 1:nrow(df)){
        df$R1[i] <- df$pre_rating[as.numeric(df$R1[i])]
        df$R2[i] <- df$pre_rating[as.numeric(df$R2[i])]
        df$R3[i] <- df$pre_rating[as.numeric(df$R3[i])]
        df$R4[i] <- df$pre_rating[as.numeric(df$R4[i])]
        df$R5[i] <- df$pre_rating[as.numeric(df$R5[i])]
        df$R6[i] <- df$pre_rating[as.numeric(df$R6[i])]
        df$R7[i] <- df$pre_rating[as.numeric(df$R7[i])]
  
}
```

# Converting again to numeric variable in order for it to work(without it wasnot working)
```{r eval = T}
df$R1 <- as.numeric(df$R1)
df$R2 <- as.numeric(df$R2)
df$R3 <- as.numeric(df$R3)
df$R4 <- as.numeric(df$R4)
df$R5 <- as.numeric(df$R5)
df$R6 <- as.numeric(df$R6)
df$R7 <- as.numeric(df$R7)
```

#Creating new variable and calculating mean to populate opponent avg score
```{r eval = T}

df["oppoAvg"]<- numeric(64)

for (i in 1:nrow(df)) {
  df$oppoAvg[i] <- round(rowMeans(df[i,6:12],na.rm=T))
}
```

#Creating final data frame with only required variables and outputing to a CSV file
```{r eval = T}
df <- df[,c(2,3,4,5,13)]
kable(df, digits = getOption("digits"), caption = "Final Table", escape = TRUE)
write.csv(df, file = "C:/Users/upalchow/Desktop/cuny_sps_fall2016/Data-607/MSDA-607/tournamentinfo.csv")
```








