---
title: "Tidy Data"
author: "Upal Chowdhury"
date: "September 27, 2016"
output: 
        html_document:
          collapsed: TRUE
          theme: cerulean  
          highlight: tango  
---
```{r eval=T,message = FALSE}
library(RCurl)
library(data.table)
library(plotly)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(xml2)
library(rvest)
library(RColorBrewer)
library(reshape2)
library(pander)
library(XML) 
library(RCurl)
library(data.table)
```

#First dataset
###https://github.com/uchow/MSDA-607/blob/master/Projects/project2/Datafiles/RatesDeaths_AllIndicators.csv
####*Tidying this UNICEF datasets to identify Mortality based on country and type of death*
```{r eval= T, message = FALSE}
data1 <- read.csv("C:/Users/upalchow/Desktop/cuny_sps_fall2016/Data-607/data/cms/RatesDeaths_AllIndicators.csv", stringsAsFactors = F,header=T)
#Replacing all the NAs to 0 so it can be aggregated
data1[is.na(data1)] <- 0

#Subsetting dataset based on Median and leaving the upper and lower bound
df1 <- subset(data1,data1$Uncertainty.bounds.=="Median")

df2 <- data.frame(df1)
attach(df2)
# Creating long format based on year
d <- df2%>%gather(year,value,c(U5MR.1950:Neonatal.Deaths.2015))

#Extarcting year from the typeof deth column so a new year column can be created
d1 <- unlist(str_extract_all(d$year,"\\d{4}"))

#Replacing the year as year is extarcted above
final <- gsub("\\.([0-9]){4}","",as.character(d$year)) %>% data.frame(cbind(d,d1))

#Changing column name to more meaningful name
colnames(final)[1] <- "Type"
colnames(final)[7] <- "Year"

#Creating final tidy data set that is analysis ready
final <- final%>%data.frame()%>%select(Type,CountryName,Year,value)%>%
  group_by(Year)%>%arrange(desc(Year))
pander(tail(final, n = 6))

#calculating infant deaths based on country in year of 2000
tope10_country <- subset(final,Type=="Infant.Deaths" & final$Year=="2000")%>%data.frame()%>%
  arrange(desc(value))%>%top_n(10)

pander(head(tope10_country, n = 10))
```

#Second dataset
###https://raw.githubusercontent.com/uchow/MSDA-607/master/Projects/project2/Datafiles/USCensus.csv
####*This Census data is cleaned up to see whats the population growth in Kentucky*
```{r eval = T}
data4 <- fread('https://www.census.gov/popest/data/intercensal/cities/files/SUB-EST00INT.csv')
attach(data4)

#Subsetting the that only includes information about Kentucky
data_filter <- subset(data4,STNAME=="Kentucky")%>%
  data.frame()%>%
  select(STNAME,contains("POPESTIMATE"))%>%
  gather(Year,Value,c(2:12))

#Replacing all the aplpha character from the year column and changing to numeric
data_filter$Year <- as.numeric(gsub("[[:alpha:]]+","",data_filter$Year))

#Calculating percent rank and selecting top rows to incluce data from 2000-2010
data_filter1 <- data_filter%>%arrange(desc(Value))%>%top_n(11)%>%arrange(Year)%>%
  mutate(percrank=(rank(Value)/length(Value))*100)

#Plotting to see the percentage change 
g2 <- ggplot(data_filter1, aes(x = Year, y = percrank)) + geom_point() + geom_smooth(method="lm")+labs(x = "Year", y = "percentrank", title = "%increase (2000-2010)")

ggplotly(g2 )

```

#Third dataset
###https://github.com/uchow/MSDA-607/blob/master/Projects/project2/Datafiles/NHE2014.csv
####*Tidying the dataset to see how medicare expense has increased over the years*
```{r eval = T}
data3 <- read.csv("C:/Users/upalchow/Desktop/cuny_sps_fall2016/Data-607/data/cms/NHE2014.csv", stringsAsFactors = F,header=T,skip = 1)

#Tranposing the data to make rows to column
data3 <- t(data3)

#Extracting the year column, cleaning up then added back to the data frame
colnames(data3)<- data3[1,]
data3 <- data3[-1,]
year <-  rownames(data3) 
year <- data.frame (as.integer(str_replace_all(year,"X","")))
dt <- cbind(year,data3)

#Get rid of the unneceesary row that appeared to be a column
rownames(dt) <- NULL

#Changing columns to character type
dt[] <- lapply(dt, as.character)

#Replacing all the empty spaces in the column names
cols <- str_replace_all(as.character(colnames(dt))," ","")
colnames(dt) <- cols

#Subsetting datasets only with Medicare
dt_sub <- dt[,which(names(dt) == "Medicare")]

#Creating the daat frame with year column and converting it to integer and subsetting only necessary columns
dt_sub <- data.frame(cbind(dt_sub[],dt$as.integer.str_replace_all.year...X.......))
dt_sub <- dt_sub[-c(1:6),]
dt_sub$year <- as.integer(as.character(dt_sub$dt.as.integer.str_replace_all.year...X.......)) 
dt_sub <- dt_sub[,-18]

#Replacing "-" and "," from data frame
dt_sub <- as.data.frame(lapply(dt_sub, function(x) gsub("-","0",x)))
dt_sub <- as.data.frame(lapply(dt_sub, function(x) gsub(",","",x)))
dt_sub <- data.frame(lapply(dt_sub, function(x) as.numeric(as.character(x))))
dt_sub <- dt_sub[,-c(1,15)]

#Creating new column by adding across the rows and selecting only year and total to see the change
dd <- dt_sub%>%data.frame()%>%transform(dt_sub,total=rowSums(dt_sub[1:16]))%>%select(year,total)
g <- ggplot(dd, aes(x = year, y = total)) + geom_point() + geom_smooth(method="lm") + 
  labs(x = "Year", y = "Total Medicare spending", title = "Medicare Expenditure (1960-2014) ") + theme(plot.title = element_text(size=20, face="bold", vjust=2))
ggplotly(g )


